---
title: Scatterplot
author: Jonas Weller
date: '2017-09-28'
slug: scatterplot
categories: []
tags: []
---

A scatter plot is a set of points plotted on a horizontal and vertical axes. It enables us two compare two sets of data.

***

First, we load our libraries and switch off error messages: 
```{r warning=FALSE, message=FALSE}
library(Lahman)
library(sqldf)
library(ggplot2)
```

***

Then, we identified what we are looking for - career homeruns and strikeouts from players who had more than 400 homeruns:
```{r}
query<-"SELECT playerID, sum(HR) AS career_HR,sum(SO) AS career_SO
FROM Batting
GROUP BY playerID
HAVING sum(HR)>=400"
sqldf(query)
```

***

Next, we learnt how to save the results as a varible:
```{r}
query<-"SELECT playerID, sum(HR) AS career_HR,sum(SO) AS career_SO
FROM Batting
GROUP BY playerID
HAVING sum(HR)>=400"
result<-sqldf(query)
```
Now, I can just type "result" in the next step because that is where the results of the query are saved.

***

Lastly, we visualized the data stored in "result":
```{r}
ggplot()+
  geom_point(data=result,aes(x=career_SO,y=career_HR),size=3,color="blue")+
  ggtitle("Career Strikeouts VS Homeruns for Great Hitters")+
  xlab("Career Strikeouts")+
  ylab("Career Homeruns")
```


The aes bracket includes what columne should be on which axis. It also specifies the size and color of the points. 

The ggtitle line specifies the headline, whereas the xlab/ylab lines specify the axes labeling. 

