---
title: Time Series Plot
author: Jonas Weller
date: '2017-09-09'
slug: time-series-plot
categories: []
tags: []
---

A Time Series Plot is displays values against time. Time is unfolding along the x-axis. THe y-axis, on the other hand, has some other variable and we can see how it changes over time.  

<!--more-->

***

Like before, we have to load our databases and switch off error messages first:
```{r warning=FALSE, message=FALSE}
library(Lahman)
library(sqldf)
library(ggplot2)
```

***

This time, we want to illustrate Babe Ruth's homerun totals throughout the years. 
```{r}
query<-"SELECT yearID, HR
FROM Batting
WHERE playerID='ruthba01'"
sqldf(query)
```

***

Storing data in "results":
```{r}
query<-"SELECT yearID, HR
FROM Batting
WHERE playerID='ruthba01'"
result<-sqldf(query)
```


***

Visualizing the data on a time series plot:
```{r}
ggplot()+
  geom_line(data=result,aes(x=yearID,y=HR))+
  geom_point(data=result,aes(x=yearID,y=HR))+
  ggtitle("Ruth's Homerun Totals Through The Years")+
  xlab("Years")+
  ylab("Homeruns")
```

