---
title: Barplot
author: Jonas Weller
date: '2017-10-05'
slug: barplot
categories: []
tags: []
---

A Barplot is a graph drawn using rectangular bars to show how large each value is. 

***

Like before, we have to load our databases and switch off error messages first:
```{r warning=FALSE, message=FALSE}
library(Lahman)
library(sqldf)
library(ggplot2)
```

***

Next, we have to extract the data and store it in "result":
```{r}
query<-"SELECT name,HR
FROM Teams 
WHERE yearID=1980
ORDER BY HR"
result<-sqldf(query)
```

***

We need to set the factor first so that our barplot will be in order from most to fewest homeruns. Moreover, we add them together by saving them in themselves:
```{r}
result$name<-factor(result$name, levels=result$name)
```

***

Now, we set everything up to visualize the data in a Barplot:
```{r}
ggplot()+
  geom_bar(data=result,aes(x=name,y=HR),stat='identity',color='blue',fill='white')+
  coord_flip()+
  ylab('homeruns')+
  xlab('team')+
  ggtitle('1980 Team Homerun Distribution')
```

Remember, that we have swtiched the axes with "coord_flip()". That means we also have to switch the axes when we want to name them. 
